### 2015-05-27 doc/thesis/typedlua.tex
Fixing the text for bibliographic data in the PUC template

Lua has a mechanism for self-like (or JavaScript-like) delegation of
missing table fields.
After the call \texttt{setmetatable(t1, \{ \string_\string_index = t2 \})},
Lua looks up in \texttt{t2} for any missing fields of \texttt{t1}.
As we mentioned in Section \ref{sec:statistics},
Lua programmers often use this mechanism to simulate classes.
We will use the following example to discuss this feature:
\begin{verbatim}
    local Shape = { x = 0.0, y = 0.0 }
    const function Shape:new (x:number, y:number):self
      local s:self = setmetatable({}, { __index = self })
      s.x = x
      s.y = y
      return s
    end
    const function Shape:move (dx:number, dy:number):()
      self.x = self.x + dx
      self.y = self.y + dy
    end
    return Shape
\end{verbatim}

@@

Note that \texttt{Shape} has a \emph{fixed} table type, because it
describes the type of the class \texttt{Shape}, but \texttt{shape1}
and \texttt{shape2} have \emph{closed} table types, because they
describe the type of objects from the class \texttt{Shape}.
Now, we will see that we need \emph{fixed} table types to allow
\texttt{setmetatable} to simulate single inheritance.
We use the following example to discuss single inheritance in Typed Lua:
\begin{verbatim}
    local Shape = require "shape"
    local Circle = setmetatable({}, { __index = Shape })
    Circle.radius = 0.0
    const function Circle:new (x:number,
                               y:number,
                               radius:value):self
      local c:self = setmetatable(Shape:new(x, y),
                                  { __index = self })
      c.radius = tonumber(radius) or 0.0
      return c
    end
    const function Circle:area ():number
      return math.pi * self.radius * self.radius
    end
    return Circle
\end{verbatim}

>>>>

Lua has a mechanism for self-like (or JavaScript-like) delegation of
missing table fields.
After the call \texttt{setmetatable(t1, \{ \string_\string_index = t2 \})},
Lua looks up in \texttt{t2} for any missing fields of \texttt{t1}.
As we mentioned in Section \ref{sec:statistics},
Lua programmers often use this mechanism to simulate classes.
We will use the following example to discuss this feature:
\begin{verbatim}
    local Shape = { x = 0.0, y = 0.0 }

    const function Shape:new (x:number, y:number):self
      local s:self = setmetatable({}, { __index = self })
      s.x = x
      s.y = y
      return s
    end

    const function Shape:move (dx:number, dy:number):()
      self.x = self.x + dx
      self.y = self.y + dy
    end

    return Shape
\end{verbatim}

@@

Note that \texttt{Shape} has a \emph{fixed} table type, because it
describes the type of the class \texttt{Shape}, but \texttt{shape1}
and \texttt{shape2} have \emph{closed} table types, because they
describe the type of objects from the class \texttt{Shape}.
Now, we will see that we need \emph{fixed} table types to allow
\texttt{setmetatable} to simulate single inheritance.
We use the following example to discuss single inheritance in Typed Lua:
\begin{verbatim}
    local Shape = require "shape"

    local Circle = setmetatable({}, { __index = Shape })

    Circle.radius = 0.0

    const function Circle:new (x:number,
                               y:number,
                               radius:value):self
      local c:self = setmetatable(Shape:new(x, y),
                                  { __index = self })
      c.radius = tonumber(radius) or 0.0
      return c
    end

    const function Circle:area ():number
      return math.pi * self.radius * self.radius
    end

    return Circle
\end{verbatim}
